Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-03-03 reports/manuscript_content.Rmd
Rerender report

Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved and the intrusion into society. Our findings showed that the impact of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition). The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each acitivty for potential harms and benefits. However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen time, with less emphasis on measures that aggregate screen time and instead focus on the content and environment in which the exposure occurs.

>>>>

Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved and the growing pervasiveness into society. Our findings showed that the impact of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition). The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits. However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen time, with less emphasis on measures that aggregate screen time and instead focus on the content, context, and environment in which the exposure occurs.

### 2022-03-03 reports/manuscript_papaja.Rmd
Rerender report

documentclass     : "apa6"
classoption       : "man"
csl               : vancouver-brackets-meta.csl
output            : papaja::apa6_pdf
nocite            : "`r params$nocite_list`"
params:
  render_img: true
  nocite_list : true
  inc_tabs: false
---

>>>>

documentclass     : "apa6"
classoption       : "man"
csl               : vancouver-brackets-meta.csl
output            : papaja::apa6_word
nocite            : "`r params$nocite_list`"
params:
  render_img: true
  nocite_list : true
  inc_tabs: false
---
